The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-07-23 article.tex
Removed some template code
Added missing periods

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CirkularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & 1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & 1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & 1.6.0 ?     & NA%
\footnote[2]{The Lingofingerprinter does not have a default size}               
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & 1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           \\

@@

%    Here is an example of a \emph{small} table in \LaTeX\ using  
%    \verb|\tabular{...}|. This is where the description of the table 
%    should go. \par \mbox{}
%    \par
%    \mbox{
%      \begin{tabular}{|c|c|c|}
%        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
%        A1 & B2  & C3 \\ \hline
%        A2 & ... & .. \\ \hline
%        A3 & ..  & .  \\ \hline
%      \end{tabular}
%      }
%  \subsection*{Table 2 - Sample table title}
%    Large tables are attached as separate files but should
%    still be described here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Additional Files              %%

%\section*{Additional Files}
%  \subsection*{Additional file 1 --- Sample additional file title}
%    Additional file descriptions text (including details of how to
%    view the file, if it is in a non-standard format or the file extension).  This might
%    refer to a multi-page table or a figure.
%
%  \subsection*{Additional file 2 --- Sample additional file title}
%    Additional file descriptions text.

>>>>

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CirkularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded.} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & 1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & 1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & 1.6.0 ?     & NA%
\footnote[2]{The Lingofingerprinter does not have a default size.}
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & 1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           \\

@@
